Hazelnut: A Bidirectionally Typed \\ Structure Editor Calculus

### 2016-10-07 formally.tex
typo

The approach that we take leaves the system unchanged. Instead, we define predicates over \emph{derivations} of the expression action judgements that excludes those derivations that apply subsumption prematurely, i.e. when another rule could have been applied. We call such derivations \emph{subsumption-minimal derivations}. We can establish determinism for subsumption-minimal derivations.
\begin{theorem}[Expression Action Determinism] ~
  \begin{enumerate}[itemsep=0px,partopsep=0px,topsep=0px]
  \item If $\hsyn{\hGamma}{\removeSel{\zexp}}{\htau}$ and
    $\mathcal{D}_1 : \performSyn{\hGamma}{\zexp}{\htau}{\alpha}{\zexp'}{\htau'}$ and
    $\mathcal{D}_2 : \performSyn{\hGamma}{\zexp}{\htau}{\alpha}{\zexp''}{\htau''}$ and $\subminsyn{\mathcal{D}_1}$ and $\subminsyn{\mathcal{D}_2}$ then
    $\zexp' = \zexp''$ and $\htau' = \htau''$.
  \item If $\hana{\hGamma}{\removeSel{\zexp}}{\htau}$ and
    $\mathcal{D}_1 : \performAna{\hGamma}{\zexp}{\htau}{\alpha}{\zexp'}$ and
    $\mathcal{D}_2 : \performAna{\hGamma}{\zexp}{\htau}{\alpha}{\zexp''}$ and $\subminana{\mathcal{D}_1}$ and $\subminana{\mathcal{D}_2}$ then $\zexp' =
    \zexp''$.
  \end{enumerate}
\end{theorem}

>>>>

The approach that we take leaves the system unchanged. Instead, we define predicates over \emph{derivations} of the expression action judgements that exclude those derivations that apply subsumption prematurely, i.e. when another rule could have been applied. We call such derivations \emph{subsumption-minimal derivations}. We can establish determinism for subsumption-minimal derivations.
\begin{theorem}[Expression Action Determinism] ~
  \begin{enumerate}[itemsep=0px,partopsep=0px,topsep=0px]
  \item If $\hsyn{\hGamma}{\removeSel{\zexp}}{\htau}$ and
    $\mathcal{D}_1 : \performSyn{\hGamma}{\zexp}{\htau}{\alpha}{\zexp'}{\htau'}$ and
    $\mathcal{D}_2 : \performSyn{\hGamma}{\zexp}{\htau}{\alpha}{\zexp''}{\htau''}$ and $\subminsyn{\mathcal{D}_1}$ and $\subminsyn{\mathcal{D}_2}$ then
    $\zexp' = \zexp''$ and $\htau' = \htau''$.
  \item If $\hana{\hGamma}{\removeSel{\zexp}}{\htau}$ and
    $\mathcal{D}_1 : \performAna{\hGamma}{\zexp}{\htau}{\alpha}{\zexp'}$ and
    $\mathcal{D}_2 : \performAna{\hGamma}{\zexp}{\htau}{\alpha}{\zexp''}$ and $\subminana{\mathcal{D}_1}$ and $\subminana{\mathcal{D}_2}$ then $\zexp' =
    \zexp''$.
  \end{enumerate}
\end{theorem}
